\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[british]{babel} % Ensures British English conventions
\usepackage{geometry}
\geometry{
    a4paper,
    margin=1in,
}
\usepackage{fancyhdr}
\pagestyle{plain} % Simple header/footer
\usepackage{hyperref}

% Define custom commands for personal details
\newcommand{\myname}{Zaher Faruk}
\newcommand{\myphone}{07553064043}
\newcommand{\myemail}{zaherfaruk04@gmail.com}
\newcommand{\mylinkedin}{\url{linkedin.com/in/zaher-faruk/}}

\begin{document}

\begin{flushleft}
    \myname \\
    \myphone \\
    \myemail \\
    \mylinkedin \\
    \vspace{0.5cm}
    \today
\end{flushleft}

\vspace{1cm}

\begin{flushleft}
    The Graduate Recruitment Team \\
    Arcadis \\
    [Insert Arcadis Address/Location if known, otherwise use general] \\
    London, United Kingdom
\end{flushleft}

\vspace{1cm}

\section*{Subject: Application for Graduate Quantity Surveyor - GROW Programme}

Dear Hiring Team,

I am writing to express my enthusiastic interest in the Graduate Quantity Surveyor position within Arcadis's GROW programme, as advertised. The opportunity to contribute to sustainable design and consultancy, whilst leveraging my strong analytical foundation, aligns perfectly with my professional aspirations.

As a final-year BSc (Hons) Physics student from The University of Salford, I recognise that my degree is non-RICS accredited. However, I am strongly encouraged by Arcadis's openness to supporting graduates from analytical backgrounds, including **Statistics, Data Processing, and Artificial Intelligence**, to achieve chartership. My academic and project experience directly reflects the key quantitative and problem-solving skills essential for a modern Cost Consultant.

My technical experience demonstrates a high level of **Analytical Thinking** and proficiency with complex data:
\begin{itemize}
    \item \textbf{Data Analysis and Modelling:} My work with the Lennard-Jones Potential Plotting project involved using Python, NumPy, and Matplotlib for **Mathematical Modelling** and data processing; these skills are directly transferable to cost estimation, budget monitoring, and providing **cost insights** utilising data, as required by the role.
    \item \textbf{Systematic Problem Solving:} Projects such as Producing and Engineering a Drone required intensive **Troubleshooting and Debugging** in both C++ software and hardware, showcasing resilience and a practical approach to resolving complex system issues.
    \item \textbf{Simulation and Complex Dynamics:} The Non-Analytic Basins and Chaotic System Simulation project using MATLAB highlights my ability to handle numerical solutions and visualise complex dynamics, a proxy for managing intricate project lifecycles and financial data sets.
\end{itemize}

Beyond technical competence, I have also cultivated the necessary interpersonal and professional skills:
\begin{itemize}
    \item \textbf{Team Player \& Communication:} My experience as an Office Administrator at the Leap Family Contact Centre required daily administrative and operational support, demanding excellent **organisational** and **communication skills** to liaise effectively and maintain processes.
    \item \textbf{Consultative Approach:} My background in Physics provides a structured and logical approach to problem-solving, enabling me to quickly assimilate technical knowledge and use it to **influence and consult stakeholders**, aligning with the consultant role accountabilities.
\end{itemize}

I am eager to embark on a career where I can apply my quantitative discipline to the commercial and transformational projects Arcadis delivers. I am fully committed to the structured 3-year GROW programme and look forward to developing the skills necessary to become an experienced professional in Cost Consultancy.

Thank you for considering my application. I am available for interview and look forward to the possibility of joining Arcadis and helping to create a lasting legacy.

Yours sincerely,

Zaher Faruk

\end{document}
