\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% Personal info
\name{Zaher}{Faruk}
\phone[mobile]{07553064043}
\email{zaherfaruk04@gmail.com}
\social[linkedin]{zaher-faruk}
\social[github]{ZaherFaruk04}

\begin{document}

\recipient{Recruitment Team}{BAE Systems Naval Ships\\Scotstoun, Glasgow}
\date{4 June 2025}
\opening{Dear Recruitment Team,}
\closing{Best regards,}
\makelettertitle

I am writing to express my interest in the Graduate Naval Ships Electrical Engineer role at BAE Systems. As a final-year Physics student at the University of Salford, I have a strong foundation in electronics, data analysis, and system-level problem solving - all skills I am excited to apply to real-world naval defence projects.

During my second year, I led the design and construction of a working drone, building its electronic systems and programming the flight controller using Arduino and C++. I designed custom hardware interfaces, assembled the circuit components, and implemented real-time control algorithms. This hands-on experience helped me develop confidence in testing, debugging, and fault diagnosis - especially when working with embedded systems and sensor inputs under realistic operating conditions.

My academic background has given me a broad technical base, including simulation and modelling using MATLAB and Python, as well as project experience involving circuit behaviour, data capture, and analysis. I’ve also developed strong written communication skills through lab reports and collaborative projects.

What attracts me to this role is the opportunity to contribute to the design and testing of cutting-edge warship systems and play a role in maintaining and evolving critical defence technologies. I’m excited by the scale and complexity of naval engineering at BAE Systems and the chance to work alongside experienced engineers on multidisciplinary projects.

Thank you for considering my application. I look forward to the opportunity to support your engineering teams and grow within BAE’s Naval Ships division.

\makeletterclosing

\end{document}
