\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic} % Options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}    % Options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[scale=0.75]{geometry} % Adjust the page margins
\setlength{\hintscolumnwidth}{3cm} % Width of the date column

% Personal info
\name{Zaher}{Faruk}
\phone[mobile]{07553064043}
\email{zaherfaruk04@gmail.com}
\social[linkedin]{zaher-faruk}
\social[github]{ZaherFaruk04}

\begin{document}

\recipient{Recruitment Team}{BAE Systems Digital Intelligence\\London, United Kingdom}
\date{4 June 2025}
\opening{Dear Recruitment Team,}
\closing{Best regards,}
\makelettertitle

I am writing to apply for the Graduate Digital Intelligence Security Consultant role at BAE Systems. As a final-year Physics student at the University of Salford with a strong interest in cybersecurity and emerging technologies, I am keen to help organisations manage digital threats and build secure systems.

One of my most impactful projects was building a working drone from scratch as part of a university team. I developed its flight control system using Arduino and C++, implemented real-time response logic, and troubleshot both hardware and software issues. I also designed custom components using Fusion 360 and assembled the full circuit, including motors and sensors. The project gave me hands-on experience in debugging complex systems - a skill I believe is highly relevant to cybersecurity work.

I’ve also been working with quantum computing platforms such as IBM Quantum and Azure Quantum, and have completed simulations in MATLAB and Python as part of my coursework. Earlier, I worked as a computer technician, gaining practical experience in securing and testing systems during repair.

What excites me about this role is the chance to contribute to meaningful digital security projects at BAE Systems while continuing to grow professionally. I would welcome the opportunity to bring my technical mindset, problem-solving ability, and drive to your team.

Thank you for considering my application.

\makeletterclosing

\end{document}
