\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{url}
\usepackage{fancyhdr}

% Set document margins
\geometry{
 a4paper,
 total={170mm,257mm},
 left=25mm,
 right=25mm,
 top=25mm,
 bottom=25mm,
 }

% Remove page numbers
\pagestyle{empty}

% Define custom commands for personal info
\newcommand{\myname}{Zaher Faruk}
\newcommand{\myphone}{0755304043}
\newcommand{\myemail}{zaherfaruk04@gmail.com}
\newcommand{\mylinkedin}{\url{linkedin.com/in/zaher-faruk/}}

\begin{document}

% --- Sender Information ---
\begin{flushright}
\myname \\
\myphone\ | \myemail \\
\mylinkedin \\
\today
\end{flushright}

% --- Recipient Information (Placeholder) ---
\vspace{1em}
\noindent
Hiring Team \\
Obsidian Security \\
 \\
United Kingdom

\vspace{1em}
\noindent
Dear Obsidian Security Hiring Team,

\vspace{1em}
I am writing to express my strong interest in the Graduate Software Engineer position. As a recent Physics graduate, I have developed a solid foundation in complex problem-solving and possess practical experience with the programming languages and systems relevant to this role. I am motivated by the prospect of building real-world security technology.

The opportunity to explore multiple areas of software engineering including data engineering, system design, and security engineering perfectly aligns with my commitment to versatile skill development. My background makes me an ideal fit for a role that values both analytical depth and technical curiosity.

\vspace{0.5em}
\noindent
\textbf{Relevant Experience and Skills:}
\begin{itemize}
    \item \textbf{Programming and Data:} My Lennard-Jones Potential Plotting project utilised Python, NumPy, and Pandas for mathematical modeling, data processing, and visualization. These are directly applicable skills for developing data pipelines and analytics systems.
    \item \textbf{System Development:} My drone project involved developing real-time control algorithms in C++ for the Arduino platform, demonstrating my ability to handle system-level logic, debugging, and hardware integration.
    \item \textbf{Cloud and Modern Tech:} I have gained hands-on familiarity with cloud environments through my quantum computing project, which involves platforms like Microsoft Azure and IBM Quantum, showing my adaptability to new and complex technologies.
    \item \textbf{Analytical Problem-Solving:} My Physics degree and projects, such as the Chaotic System Simulation using MATLAB's ODE solver, confirm my rigorous analytical approach, a key trait for effective software and security engineering.
\end{itemize}

\vspace{0.5em}
I am keen to join a collaborative team that supports continuous learning and contributes to a critical SaaS security platform. I am confident in my eagerness to learn and my ability to contribute meaningfully to your engineering goals.

\vspace{1em}
Thank you for considering my application. I look forward to the possibility of discussing this exciting opportunity further.

\vspace{1em}
\noindent
Sincerely, \\
Zaher Faruk

\end{document}
