\documentclass[a4paper,11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{lmodern}
\usepackage{hyperref}

\signature{Zaher Faruk}
\address{
    Zaher Faruk \\
    zaherfaruk04@gmail.com \\
    07553064043 \\
    \href{https://linkedin.com/in/zaher-faruk}{linkedin.com/in/zaher-faruk} \\
    \href{https://github.com/ZaherFaruk04}{github.com/ZaherFaruk04}
}
\date{26 June 2025}

\begin{document}

\begin{letter}{Stantec Recruitment Team\\Stantec UK}

\opening{Dear Stantec Recruitment Team,}

I’m writing to express my interest in the Graduate Electrical Engineer role based in your Manchester office. I’m currently completing my BSc in Physics at the University of Salford (predicted 2:1) and I’m excited by the opportunity to begin my engineering career at a company committed to sustainability and innovation.

During my second year, I was part of a team project where we designed and engineered a working drone. My role involved programming the control system in C++, designing and assembling the electronics using Arduino, and troubleshooting both hardware and software challenges. The project sharpened my hands-on electrical skills and gave me a real appreciation for collaborative engineering and practical problem-solving.

Beyond that, I’ve worked on projects involving circuit design, simulation, and data visualisation using tools like Python and MATLAB. I’m also currently expanding my skills in CAD and modelling, and I’m keen to learn Revit, Dialux and other building services software tools as part of your graduate programme.

I’m a motivated and curious learner with a real interest in sustainable design. I’d welcome the chance to grow within a supportive team like Stantec’s, where I can contribute from day one while developing professionally.

\closing{Kind regards,}

\end{letter}

\end{document}
